Robust Bayesian Analysis of Causal Inference Problems

### 2024-03-21 JASA-template.tex
Another note.

In theory, both $\mathbb{E}(Y_i\mid T_i=1)$ and $\mathbb{E}(Y_i\mid T_i=0)$ exist.
However, we cannot observe them simultaneously, since we cannot `treat' and `not treat' the same individual at the same time.
What we can observe is the average causal effect of the treatment,
by calculating the averaged
outcome of all the subjects that received the treatment and
all the subjects that remained as control:
\begin{align}
  \hat{\delta} \coloneqq 
  \frac{\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=1)-\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=0)}{n}.
\end{align}
However, this relies on an important assumption that the treatment effect
on the $i$-th subject given that they received the treatment is the same as the (counterfactual) treatment effect when they remain as control \cite{winship99}.

>>>>

In theory, both $\mathbb{E}(Y_i\mid T_i=1)$ and $\mathbb{E}(Y_i\mid T_i=0)$ exist.
However, we cannot observe them simultaneously, since we cannot `treat' and `not treat' the same individual at the same time.
What we can observe is the average causal effect of the treatment,
by calculating the averaged
outcome of all the subjects that received the treatment
minus that of all the subjects that remained as control:
\begin{align}
  \hat{\delta} \coloneqq 
  %\frac{\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=1)-\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=0)}{n}
  %%% MT to TB check if this is correct, it seems a bit simpler to write like this
  \frac{\sum_{i=1}^n Y_iT_i-\sum_{i=1}^n Y_i(1-T_i)}{n}.
\end{align}
%%% MT to TB: is it assumed both groups have the same size, namely n/2? or not?
However, this relies on an important assumption that the treatment effect
on the $i$-th subject given that they received the treatment is the same as the (counterfactual) treatment effect when they remain as control \cite{winship99}.
